### 2017-05-09 paper1.tex
Add files via upload

\section{Introduction}
Thermal infrared (TIR) remote sensing of land surface temperature (T\textsubscript{surf}) has emerged as a primary research focus in climatology, as researchers seek to better describe spatiotemporal patterns of T\textsubscript{surf} globally and better understand how anthropogenic modification of earth's surface influences land T\textsubscript{surf} and impacts climate at various scales. Over the last two decades, the application of thermal remote sensing to study surface climates has expanded significantly. Thermal remote sensing of earth's surface has applications over a wide range of disciplines: from informing micro-, urban-, and global-scale climate models, to aiding decision making and mitigation praxis with respect to climate change and the \gls{uhi}.

Within urban climatology, a combination of satellite, aerial, and ground-based thermal remote sensors have been integral in elucidating the spatial \citep{Roth1989}, temporal \citep{Peng2012}, and geometric \citep{Voogt1997} effects of the built environment on land T\textsubscript{surf}; in evaluating and partitioning urban surface energy balances \citep{BastiaanssenW.G.M.1998, Yamaguchi2005} and; in characterizations of the relationship between surface and \gls{blayer} air temperatures (T\textsubscript{air}) \citep{Stoll1992}. These advances have been aided by substantial improvements in sensor spatial, spectral, and radiometric resolutions, and by the proliferation of both large-scale public satellite remote sensing campaigns and low-cost aerial and near-ground thermography. However, in spite of it's widespread usage, several questions concerning the use and validity of urban remote thermal remote sensing, first posed in \citet{Roth1989}, have yet to be sufficiently answered, viz,

@@

\noindent In this paper, we seek to examine question two by introducing and evaluating a method for atmospheric correction of near-ground hemispherical TIR --- measured via \gls{pyrg} --- for hemispherical radiometric temperature (T\textsubscript{hem, r}) retrieval. These measures are common to most urban energy balance assessments and thus constitute a hitherto untapped method for urban T\textsubscript{surf} analysis. A companion paper responds to question one through an analysis of an 8-month climatology of T\textsubscript{hem, r} and derived surface UHI magnitudes (sUHI), to quantify geometric and temporal biases across multiple methods for remote sensing of urban T\textsubscript{surf}.

@@

Although most thermal remote sensors operate within one of the \gls{atmwind}[s] - where atmospheric effects are minimal - virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared \gls{waveband} the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal almost certainly not equal to the ground emitted signal. Spectral radiance received by a sensor at height ($z$) can be described by a function deviating from a Planck curve defined by T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation determined by the difference between Planck curves calculated from T\textsubscript{surf} and ambient T\textsubscript{air}. A radiative transfer code, such as MODTRAN \citep{Berk1987}, can be used to model the effect of the atmosphere on a remote sensed TIR signal. Radiative transfer simulations run in MODTRAN version 4.1 for two path lengths are shown in Figure \ref{spectairtsurf}, for spectral radiance emitted from a planar surface at 300 \si{kelvin} through an isothermal atmosphere at 290 \si{\kelvin}, water vapor content of 12 \si{\gram\per\meter\cubed}, and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere \citep{Kantor1962}. At both short and long path lengths, radiance in each band shows some deviation from the ground emitted signal. Larger deviations are observed at longer path lengths, where a significant portion of the resulting signal is emitted from that atmosphere, even in bands with high spectral transmittance. Long path lengths and a less transmissive atmosphere increase the potential for deviation in a remote sensed TIR signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence.

@@

Spectral transmission of longwave radiation through a given layer of atmosphere is dependent on total column absorber content (the principal broadband TIR absorbers are H\textsubscript{2}O, CO\textsubscript{2}, and to a lesser extent O\textsubscript{3}, N\textsubscript{2}O, CO, CH\textsubscript{4}, and O\textsubscript{2} \citep{Miskolczi1993}). Holding vertical absorber content constant through a layer of atmosphere, variation in band-by-band TIR transmittance with path length is greatest at urban scales (approximately 1 to 50 \si{\meter}), where transparent spectral bands can quickly become opaque with small changes in path length or absorber content - illustrated in figure \ref{spectransheight}. Thus, transmittance of TIR near the surface is highly dependent on surface-sensor geometry, instrument spectral response, and atmospheric absorber content. Indeed, accurate assessment of atmospheric influence on TIR may be most complex when measured near the surface.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{spectransheight}
	\caption{Spectral transmission of water vapor as a function of height. Run in MODTRAN 4.1 for radiance emitted from a planar surface at 300 \si{\kelvin} through an atmosphere with water vapor content of 8 \si{\gram\per\meter\cubed}. Sampled at heights of 1, 5, 10, 15, 20, 25, and 30 \si{\meter}.}
	\label{spectransheight}
\end{figure}

@@

\noindent where \(\epsilon\)\textsubscript{\( \lambda \)} is spectral surface emissivity, \(\tau\)\textsubscript{\( \lambda \)} is spectral "slab" transmittance through the layer between the emitting surface $( z  = 0) $ and $ z $. Directional radiances upwelling from the atmosphere $R^\uparrow_{atm}$, and the surface $R^\uparrow_0$, and downwelling from the sky $R^\downarrow_{sky}$, can be described spectrally or integrated over a waveband bounded by \(\lambda_1\) and \(\lambda_2\) as

@@

\begin{equation}
\label{stefb1}
T_{hem,~ b} = \sqrt[4]{\frac{L_z}{\overline{r}\sigma}}
\end{equation}

\noindent where $ \sigma $ is the Stefan-Boltzmann constant and $ \overline{r} $ is Planck weighted mean broadband sensor response computed as,

\noindent with $ R(\lambda) $ computed from a Planck function at an approximated emitter temperature.

A \textit{directional brightness temperature} T\textsubscript{bright} $(\theta, \phi)$ from some viewing able described $\theta$ and $\phi$ by can be inferred from directional radiance via equation \ref{stefb1} by replacing $ L_z $ with $L_z'$ multiplied by a constant. This method is commonly used to infer T\textsubscript{bright} $(\theta, \phi)$ from infrared thermometers (IRT) operating over the atmospheric window - where atmospheric effects are minimal and T\textsubscript{bright} is a reasonably accurate approximation of T\textsubscript{surf}. However, constants must be calibrated for the range of expected T\textsubscript{surf} as the relationship between $ L_z $ and $L_z'$  is not perfectly linear with respect to emitter temperature.

Inversions of uncorrected $ L_z $ or \textbf{$L_z'$} yield a temperature equal to that of a blackbody emitting the same amount of radiation as detected by the sensor. Since $ L_z $ is unlikely to be equal to $ L_0 $ and, by extension,  $L_z'$ is unlikely to be equal to $L_0'$, T\textsubscript{hem, b} at $ z = 0 $ and T\textsubscript{hem, b} at $ z $ often show significant deviation based on sensor characteristics, ambient conditions, and surface-sensor geometry. Hence, T\textsubscript{bright} and T\textsubscript{hem, b} are generally considered only a rough approximation representation of radiometric, kinetic, or thermodynamic T\textsubscript{surf}.

@@

A large number of correction routines have been developed to remove atmospheric and emissivity effects from aerial and satellite TIR signals and derive accurate T\textsubscript{rad}. Methods range from simple mono-window \citep{Qin2001} and split-window \citep{Wan1996} routines for single-channel and multi-channel remote sensors, to schemes that integrate a radiative transfer code to isolate the surface emitted signal from interfering signals. Boundary conditions are standard across most correction methods: generally requiring vertical profiles of T\textsubscript{air}, humidity, pressure, and aerosol content to remove atmospheric effects, and surface radiative properties to correct for emissivity effects. However, correction methods are often instrument (or, at the very least, least platform) specific and difficult to generalize across sensor and platform types. Few methods exist for correction of ground based remote sensed TIR --- none of which are robust enough to correct irradiances measured from a near-ground wide-\gls{fov} (FOV) radiometer mounted to view rough terrain.

@@

Several multi-LOS correction routines have been developed for to remove atmospheric effects on near-ground remote sensed TIR: \citet{Meier2011} describes a correction method for oblique angled thermal imagery of urban terrain. In the method, spatially distributed LOS geometries were calculated by linking each image pixel to the corresponding 3-d coordinates of its viewpoint on a digital building model (DBM). Path lengths were then calculated as the distance between each pixel's corresponding location on the DBM and the sensor represented as the vanishing point of a 3-dimensional pyramidic projection from the sensor's location in the DBM. A pixel-by-pixel correction was then applied to remove atmospheric effects and retrieve T\textsubscript{rad} for each pixel at 30 minute intervals, resulting in a time-continuous climatology of urban T\textsubscript{rad}. However, the method uses thermal images in conjunction with a DBM to calculate path length geometries for each pixel's LOS - a technique not possible with a pyrgeometer, which returns a single integrated value over the sensor FOV. Moreover, the target instrument operates over a narrow waveband with relatively uniform spectral sensor response, reducing the magnitude and variance in atmospheric transmission over the sensor response curve. Thus, the method is not directly generalizable to correct TIR measured via pyrgeometer.

\citet{Kotani2009a} describes a method for correction of wide-FOV (pyrgeometer) TIR irradiances over a homogeneous planar surface. In this method, path lengths were calculated for six sensor heights. Radiances were then modeled using LOWTRAN initialized at $5^{\circ}$ intervals and integrated over the hemisphere to retrieve irradiances for a suite of T\textsubscript{surf}, and ambient T\textsubscript{air} and humidities. The resulting lookup table (LUT) of values is then used to correct $L_z$ and quantify atmospheric effects on remote sensed $L_z$ measured from several sensor heights. Methods outlined in Meier et al., 2011 and Kotani \& Sugita, 2009 are limited to narrow-FOV thermal imagers and planar terrain respectively. A method which combines Meier et al., 2011's representation of complex surface geometry and Kotani \& Sugita, 2009's broadband hemispherical integration is needed for atmospheric correction of urban TIR measured via downward facing pyrgeometer.

@@

With methodological generalizability in mind, a "rolling lookup table" atmospheric correction method was developed to retrieve radiometric T\textsubscript{hem, r} for a climatology of upwelling longwave irradiances measured from above the Sperrstrasse street canyon in Basel, Switzerland. The site, instrumented as a part of the Basel Urban Boundary Layer Experiment (BUBBLE) \cite{Rotach2005}, has an approximately northeast-southwest orientation and site morphology representative of local climate zone (LCZ) 2\footnote{Site surroundings can be described by the following morphological parameters: mean building height: 14.6m, plan aspect ratio: 0.54, complete aspect ratio: 1.92, local canyon aspect ratio: 1.0, and average shortwave albedo: 0.11 \cite{Rotach2005}.} \cite{Stewart2012}. LCZ classification was based on an assessment of surface characteristics in a 250m circular area extending from the Sperrstrasse tower using a 1 \si{m} raster digital building model (DBM). Thus, the morphological parameters identified in \cite{Rotach2005} are representative of a majority of the pyrgeometer footprint. Vegetation was not included in the DBM, and thus is not represented in morphological assessment or the sensor view model, however, the street canyon and surrounding area has little vegetation.

For the eight month period between December 2001 and July 2002, a triangular lattice tower was installed within the Sperrstrasse street canyon. It's location was skewed towards the southeast facing wall near the along-canyon center of the canyon. Instruments to observe a full suite of meteorological variables and fluxes of heat, mass, and momentum are mounted at various levels on the tower. Profiles of T\textsubscript{air} and humidity were measured at seven heights extending from 2.5 \si{m} to 31.5 \si{m} above the canyon floor (with the highest observation level at approximately 2.17 times mean roof level). Upwelling and downwelling short/longwave fluxes were obtained from radiometers mounted at the lowest and highest measurement levels, with an additional downward facing pyrgeometer mounted at roof level near the center of the street canyon. In addition, during a summertime intense operation period (IOP) an array of narrow-FOV IRTs was installed to sample representative individual facet surface temperatures (T\textsubscript{facet}).

The BUBBLE Sperrstrasse site was chosen for two primary reasons: 1. The site provided a long-term climatology of radiation and meteorological variables for a representative mid-latitude city. This allowed for examination of urban T\textsubscript{surf}, sUHI, and atmospheric correction magnitudes over a wide range of representative mid-latitude conditions. 2.  In inclusion of T\textsubscript{facet} over the IOP allows for investigation of the effect of sensor-surface geometry on remote sensed urban T\textsubscript{surf} for common urban T\textsubscript{surf} measurement strategies. This directional dependence of urban T\textsubscript{surf} - termed "effective anisotropy" - refers to the notion that a TIR signal upwelling from rough terrain viewed from a remote sensor changes based on the combined effects of surface-sensor-sun geometry and the convoluted, 3-dimensional structure of the urban surface \cite{Voogt1998a}. Facet surface temperatures measured during the summertime IOP allow for direct climatological comparison of T\textsubscript{hem, r} to common remote sensed representations of the urban surface constructed from weighted averages of wall (T\textsubscript{wall}), road (T\textsubscript{road}), and roof (T\textsubscript{roof}) temperatures. Table \ref{weightings} describes T\textsubscript{facet} weightings for nadir remote sensed (T\textsubscript{plan}) and complete (T\textsubscript{comp}) representations of urban surface temperature. At each time step, both T\textsubscript{hem, r} and T\textsubscript{plan} were divided by T\textsubscript{comp} and averaged over the IOP to yield normalized mean T\textsubscript{hem, r} and T\textsubscript{plan} at 30-minute intervals. Through comparison of T\textsubscript{hem, r} to T\textsubscript{plan} and T\textsubscript{comp} we investigate the effect of sensor-surface geometry on remote sensed urban T\textsubscript{surf} and quantify directional biases in common urban T\textsubscript{surf} measurements.

@@

\subsection{Modeling hemispherical irradiances}
With path length geometries calculated in SUM, irradiances are modeled for each time step using version 4.1 of the MODerate resolution atmospheric TRANsmission radiative transfer code (MODTRAN) \citep{Berk1987}. At each time-step, a range of potential temperatures is specified (T\textsubscript{spec}) based on T\textsubscript{hem, b} calculated from the measured irradiance with

@@

After the LUT is defined, at-sensor spectral radiances for each path length/zenith angle are modeled at an emissivity of 0.95 over a waveband of 0 - 2300 \si{cm^{-1}} for each T\textsubscript{spec}. Profiles of T\textsubscript{air} and humidity are retrieved from 30-minute averages of conditions observed at the Sperrstrasse site. Aerosol, trace gas absorber, and above-sensor T\textsubscript{air} and humidity conditions are defined by the mid-latitude summer standard atmosphere when daytime T\textsubscript{air, max} \textgreater 10 \si{\degreeCelsius} (the mid-latitude winter profile is substituted on days where T\textsubscript{air, max} \textless 10 \si{\degreeCelsius}) \citep{Kantor1962}.

In this method, a "typical" longwave bandpass, approximately 250 - 2300 \si{\centi\meter^{-1}} (4 - 42 \si{\micro\meter}), was extended to include much smaller wavenumber (longer wavelengths). This was done for two reasons: 1) To accurately represent spectral longwave curves for typical urban T\textsubscript{surf}, which show significant emittance in wavenumber smaller than 250 \si{cm^{-1}} (wavelengths much longer than 42 \si{\micro\meter}). 2) To replicate the spectral signal "seen" by a silicone-domed pyrgeometer, which continues to transmit radiation at wavenumber \textless 250 \si{cm^{-1}} (wavelengths \textgreater 42 \si{\micro\meter}). A "typical" longwave bandpass underestimates a pyrgeometer signal by approximately 7 - 10 \si{\watt\per\square\meter}, depending on emitter temperature. A comparison of ‘typical’ and ‘extended’ longwave bandpasses is shown in Figure \ref{dometrans}.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{dometrans}
	\caption{A comparison of dome transmittance for a Kipp \& Zonen silicone domed pyrgeometer and at-sensor radiance (T\textsubscript{surf} = 300 \si{K}, T\textsubscript{air} = 300 \si{K}, $z$ = 30 \si{m})  for "typical" and extended bandpasses.}
	\label{dometrans}
\end{figure}

@@

\noindent to yield a directional radiance $ L'_z $ for each $\theta$, with $\overline{r}$ as mean dome transmittance over a waveband of $\nu_1 $= 0 \si{cm^{-1}} to $\nu_2$ = 2300 \si{cm^{-1}}. $ L'_z (\theta) $ are then multiplied by their associated angular view factor weighting ($\Phi$) and integrated over the hemisphere to yield an irradiance $ L_z $ for the target T\textsubscript{hem, r}

@@

$L_z (T\textsubscript{spec}) $ is representative of at-sensor irradiance upwelling from the urban surface described in SUM at the target specified temperature T\textsubscript{hem, r} for the measured T\textsubscript{air}, humidity, aerosol, and trace gas profile. The process is repeated to retrieve $L_z$ for the range of potential T\textsubscript{hem, r} at the given time-step. Irradiance - T\textsubscript{hem, r} pairings are then aggregated into a LUT. Finally, the measured irradiance from BUBBLE is matched with its closest modeled irradiance to yield an atmospherically corrected, radiometric hemispherical surface temperature for the given time step. The workflow is repeated at 30-minute intervals to yield a continuous time series of T\textsubscript{hem, r}. Atmospheric correction magnitudes can then be calculated as the difference between T\textsubscript{hem, r} and T\textsubscript{hem, b}, with T\textsubscript{hem, b} calculated via:

\begin{equation}
	\label{stefboltz2}
	T_{hem,~ b} = \sqrt[4]{\frac{L_z}{\sigma}}
\end{equation}.

\section{Evaluation of the method using profiles of upwelling longwave radiation over a homogeneous planar surface} \label{sensitivity}

>>>>

\section{Introduction}

Thermal infrared (TIR) remote sensing of land surface temperature (T\textsubscript{surf}) has emerged as a primary research focus in climatology, as researchers seek to better describe spatiotemporal patterns of T\textsubscript{surf} globally and better understand how anthropogenic modification of earth's surface influences land T\textsubscript{surf} and impacts climate at various scales. Over the last two decades, the application of thermal remote sensing to study surface climates has expanded significantly. Thermal remote sensing of earth's surface has applications over a wide range of disciplines: from informing micro-, urban-, and global-scale climate models, to aiding decision making and mitigation praxis with respect to climate change and the urban heat island effect.

Within urban climatology, a combination of satellite, aerial, and ground-based thermal remote sensors have been integral in elucidating the spatial \citep{Roth1989}, temporal \citep{Peng2012}, and geometric \citep{Voogt1997} effects of the built environment on land T\textsubscript{surf}; in evaluating and partitioning urban surface energy balances \citep{BastiaanssenW.G.M.1998, Yamaguchi2005,Frey2007} and; in characterizations of the relationship between surface and boundary-layer air temperatures (T\textsubscript{air}) \citep{Stoll1992}. These advances have been aided by substantial improvements in sensor spatial, spectral, and radiometric resolutions, and by the proliferation of both large-scale public satellite remote sensing campaigns and low-cost aerial and near-ground thermography. However, in spite of it's widespread usage, several questions concerning the use and validity of urban remote thermal remote sensing, first posed in \citet{Roth1989}, have yet to be sufficiently answered, viz,

@@

\noindent In this paper, we seek to examine question two by introducing and evaluating a method for atmospheric correction of near-ground hemispherical TIR - measured via pyrgeometer - for hemispherical radiometric temperature (T\textsubscript{hem, r}) retrieval. These measures are common to most urban energy balance assessments because they are made as a part of the net radiation measurement and thus constitute a hitherto untapped method for urban T\textsubscript{surf} analysis. A companion paper responds to question one through an analysis of two long term climatologies of T\textsubscript{hem, r} and derived surface UHI magnitudes (sUHI), to quantify geometric and temporal biases across multiple methods for remote sensing of urban T\textsubscript{surf}.

@@

Although most thermal remote sensors operate within one of the atmospheric windows - where atmospheric effects are minimal - virtually any remote sensed TIR signal is subject to radiative effects from the layer of atmosphere between the surface and the sensor. Over much of the thermal infrared waveband the atmosphere emits radiation and absorbs a fraction of radiation emitted by the surface. Thus, a remote sensed TIR signal is almost certainly not equal to the ground emitted signal. Spectral radiance received by a sensor at height ($z$) can be described by a function deviating from a Planck curve defined by T\textsubscript{surf} based on the spectral transmittance of the intervening atmosphere, with the magnitude of that deviation determined by the difference between Planck curves calculated from T\textsubscript{surf} and ambient T\textsubscript{air}. A radiative transfer code, such as MODTRAN \citep{Berk1987}, can be used to model the effect of the atmosphere on a remote sensed TIR signal. Radiative transfer simulations run in MODTRAN version 4.1 for two path lengths are shown in Figure \ref{spectairtsurf}, for spectral radiance emitted from a planar surface at 300 \si{\kelvin} through an isothermal atmosphere at 290 \si{\kelvin}, water vapor content of 12 \si{\gram\per\meter\cubed}, and aerosol and trace gas profiles from the mid-latitude summer standard atmosphere \citep{Kantor1962}. At both short and long path lengths, radiance in each band shows some deviation from the ground emitted signal. Larger deviations are observed at longer path lengths, where a significant portion of the resulting signal is emitted from that atmosphere, even in bands with high spectral transmittance. Long path lengths and a less transmissive atmosphere increase the potential for deviation in a remote sensed TIR signal from the ground emitted signal, while the difference between T\textsubscript{air} and T\textsubscript{surf} determines the resulting magnitude of atmospheric influence.

@@

Spectral transmission of longwave radiation through a given layer of atmosphere is dependent on total column absorber content (the principal broadband TIR absorbers are H\textsubscript{2}O, CO\textsubscript{2}, and to a lesser extent O\textsubscript{3}, N\textsubscript{2}O, CO, CH\textsubscript{4}, and O\textsubscript{2} \citep{Miskolczi1993}). Holding vertical absorber content constant through a layer of atmosphere, variation in band-by-band TIR transmittance with path length is greatest at the scale of an urban canyon (approximately 1 to 50 \si{\meter}), where transparent spectral bands can quickly become opaque with small changes in path length or absorber content - illustrated in Figure \ref{spectransheight}. Thus, transmittance of TIR near the surface is highly dependent on surface-sensor geometry, instrument spectral response, and atmospheric absorber content. Indeed, accurate assessment of atmospheric influence on TIR may be most complex when measured near the surface.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{spectransheight}
	\caption{Spectral transmission of water vapor as a function of height. Model results from MODTRAN 4.1 for radiance emitted from a planar surface at 300 \si{\kelvin} through an atmosphere with water vapor content of 8 \si{\gram\per\meter\cubed}. Sampled at heights of 1, 5, 10, 15, 20, 25, and 30 \si{\meter}.}
	\label{spectransheight}
\end{figure}

@@

\noindent where \(\epsilon\)\textsubscript{\( \lambda \)} is spectral surface emissivity, \(\tau\)\textsubscript{\( \lambda \)} is spectral "slab" transmittance through the layer between the emitting surface $( z  = 0) $ and $ z $. Directional radiances upwelling from the atmosphere $R^\uparrow_{atm}$, and the surface $R^\uparrow_0$, and downwelling from the sky $R^\downarrow_{sky}$, can be described spectrally or integrated over a waveband bounded by \(\lambda_1\) and \(\lambda_2\) as Planck's law

@@

\begin{equation}
\label{stefb1}
T_{hem,~ b} = \sqrt[4]{\frac{L_z}{\sigma}}
\end{equation}

\noindent where $ \sigma $ is the Stefan-Boltzmann constant.

A \textit{directional brightness temperature} T\textsubscript{bright} $(\theta, \phi)$ from some viewing angle described by $\theta$ and $\phi$ can be inferred from directional radiance via equation \ref{stefb1} by replacing $ L_z $ with $L_z'$ multiplied by a constant. This method is commonly used to infer T\textsubscript{bright} $(\theta, \phi)$ from infrared thermometers (IRT) operating over the atmospheric window - where atmospheric effects are minimal and T\textsubscript{bright} is a reasonably accurate approximation of T\textsubscript{surf}. However, constants must be calibrated for the range of expected T\textsubscript{surf} as the relationship between $ L_z $ and $L_z'$  is not perfectly linear with respect to emitter temperature.

Inversions of uncorrected $ L_z $ or \textbf{$L_z'$} yield a temperature equal to that of a blackbody emitting the same amount of radiation as detected by the sensor. Since $ L_z $ is unlikely to be equal to $ L_0 $ and, by extension,  $L_z'$ is unlikely to be equal to $L_0'$, T\textsubscript{hem, b} at $ z = 0 $ and T\textsubscript{hem, b} at $ z $ often show significant deviation based on sensor characteristics, ambient conditions, and surface-sensor geometry. Hence, T\textsubscript{bright} and T\textsubscript{hem, b} are generally considered only a rough approximation representation of radiometric T\textsubscript{surf}.

@@

A large number of correction routines have been developed to remove atmospheric and emissivity effects from aerial and satellite TIR signals and derive accurate T\textsubscript{rad}. Methods range from simple mono-window \citep{Qin2001} and split-window \citep{Wan1996} routines for single-channel and multi-channel remote sensors, to schemes that integrate a radiative transfer code to isolate the surface emitted signal from interfering signals. Boundary conditions are standard across most correction methods: generally requiring vertical profiles of T\textsubscript{air}, humidity, pressure, and aerosol content to remove atmospheric effects, and surface radiative properties to correct for emissivity effects. However, correction methods are often instrument (or, at the very least, least platform) specific and difficult to generalize across sensor and platform types. Few methods exist for correction of ground based remote sensed TIR --- none of which are robust enough to correct irradiances measured from a near-ground wide-field-of-view (FOV) radiometer mounted to view rough terrain.

@@

Several multi-LOS correction routines have been developed to remove atmospheric effects on near-ground remote sensed TIR: \citet{Meier2011} describes a correction method for oblique angled thermal imagery of urban terrain. In the method, spatially distributed LOS geometries were calculated by linking each image pixel to the corresponding 3-d coordinates of its viewpoint on a digital building model (DBM). Path lengths were then calculated as the distance between each pixel's corresponding location on the DBM and the sensor represented as the vanishing point of a 3-dimensional pyramidic projection from the sensor's location in the DBM. A pixel-by-pixel correction was then applied to remove atmospheric effects and retrieve T\textsubscript{rad} for each pixel at 30 minute intervals, resulting in a time-continuous climatology of urban T\textsubscript{rad}. However, the method uses thermal images in conjunction with a DBM to calculate path length geometries for each pixel's LOS - a technique not possible with a pyrgeometer, which returns a single integrated value over the sensor FOV. Moreover, the target instrument operates over a narrow waveband with relatively uniform spectral sensor response, reducing the magnitude and variance in atmospheric transmission over the sensor response curve. Thus, the method is not directly generalizable to correct TIR measured via pyrgeometer.

\citet{Kotani2009a} describes a method for correction of wide-FOV (pyrgeometer) TIR irradiances over a homogeneous planar surface. In this method, path lengths were calculated for six sensor heights. Radiances were then modeled using the LOWTRAN \citep{Kneizys1988} radiative transfer code initialized at $5^{\circ}$ intervals and integrated over the hemisphere to retrieve irradiances for a suite of T\textsubscript{surf}, and ambient T\textsubscript{air} and humidities. The resulting lookup table (LUT) of values is then used to correct $L_z$ and quantify atmospheric effects on remote sensed $L_z$ measured from several sensor heights. Methods outlined in \citet{Meier2011} and \citet{Kotani2009a} are limited to narrow-FOV thermal imagers and planar terrain respectively. A method which combines \citet{Meier2011}'s representation of complex surface geometry and \citep{Kotani2009a}'s broadband hemispherical integration is needed for atmospheric correction of urban TIR measured via downward facing pyrgeometer.

@@

With methodological generalizability in mind, a "rolling lookup table" atmospheric correction method was developed to retrieve radiometric T\textsubscript{hem, r} for a climatology of upwelling longwave irradiances measured from above the Sperrstrasse street canyon in Basel, Switzerland. The site, instrumented as a part of the Basel Urban Boundary Layer Experiment (BUBBLE) \cite{Rotach2005}, has an approximately northeast-southwest orientation and site morphology representative of local climate zone (LCZ) 2\footnote{Site surroundings can be described by the following morphological parameters: mean building height: 14.6m, plan aspect ratio: 0.54, complete aspect ratio: 1.92, local canyon aspect ratio: 1.0, and average shortwave albedo: 0.11 \cite{Rotach2005}.} \cite{Stewart2012}. LCZ classification was based on an assessment of surface characteristics in a 250 \si{\meter} circular area extending from the Sperrstrasse tower using a 1 \si{m} raster digital building model (DBM). Thus, the morphological parameters identified in \cite{Rotach2005} are representative of a majority of the pyrgeometer footprint. Vegetation was not included in the DBM, and thus is not represented in morphological assessment or the sensor view model, however, the street canyon and surrounding area has little vegetation.

For the eight month period between December 2001 and July 2002, a triangular lattice tower was installed within the Sperrstrasse street canyon. It's location was skewed towards the southeast facing wall near the along-canyon center of the canyon. Instruments to observe a full suite of meteorological variables and fluxes of heat, mass, and momentum are mounted at various levels on the tower. Profiles of T\textsubscript{air} and humidity were measured at seven heights extending from 2.5 \si{m} to 31.5 \si{m} above the canyon floor (with the highest observation level at approximately 2.17 times mean roof level). Upwelling and downwelling short/longwave fluxes were obtained from radiometers mounted at the lowest and highest measurement levels, with an additional downward facing pyrgeometer mounted at roof level near the center of the street canyon. In addition, during a summertime intensive observation period (IOP) an array of narrow-FOV IRTs was installed to sample representative individual facet surface temperatures (T\textsubscript{facet}).

The BUBBLE Sperrstrasse site was chosen here for two primary reasons: 1. The site provided a long-term climatology of radiation and meteorological variables for a representative mid-latitude city. This allowed for examination of urban T\textsubscript{surf}, sUHI, and atmospheric correction magnitudes over a wide range of representative mid-latitude conditions. 2.  Inclusion of T\textsubscript{facet} over the IOP allows for investigation of the effect of sensor-surface geometry on remote sensed urban T\textsubscript{surf} for common urban T\textsubscript{surf} measurement strategies. This directional dependence of urban T\textsubscript{surf} - termed "effective anisotropy" - refers to the notion that a TIR signal upwelling from rough terrain viewed from a remote sensor changes based on the combined effects of surface-sensor-sun geometry and the convoluted, 3-dimensional structure of the urban surface \cite{Voogt1998a}. Facet surface temperatures measured during the summertime IOP allow for direct climatological comparison of T\textsubscript{hem, r} to common remote sensed representations of the urban surface constructed from weighted averages of wall (T\textsubscript{wall}), road (T\textsubscript{road}), and roof (T\textsubscript{roof}) temperatures. Plan and complete aspect ratios are used to derive weightings for nadir remote sensed (T\textsubscript{plan}) and complete (T\textsubscript{comp}) representations of urban surface temperature - described in Table \ref{weightings}. At each time step, T\textsubscript{hem, r} and T\textsubscript{plan} were divided by T\textsubscript{comp} and averaged over the IOP to yield normalized mean T\textsubscript{hem, r} and T\textsubscript{plan} at 30-minute intervals. Through comparison of T\textsubscript{hem, r} to T\textsubscript{plan} and T\textsubscript{comp} we investigate the effect of sensor-surface geometry on remote sensed urban T\textsubscript{surf} and quantify directional biases in common urban T\textsubscript{surf} measurements.

@@

\subsection{Modeling hemispherical irradiances}
With path length geometries calculated in SUM, irradiances are modeled for each time step using version 4.1 of the MODerate resolution atmospheric TRANsmission radiative transfer code (MODTRAN) \citep{Berk1987}. At each time-step, a range of possible temperatures is specified (T\textsubscript{spec}) based on T\textsubscript{hem, b} calculated from the measured irradiance with

@@

After the LUT is defined, at-sensor spectral radiances for each path length/zenith angle are modeled at an emissivity of 0.95 over a waveband of 0 - 2300 \si{cm^{-1}} for each T\textsubscript{spec}. Profiles of T\textsubscript{air} and humidity are retrieved from 30 \si{\minute} averages of conditions observed at the Sperrstrasse site. Aerosol, trace gas absorber, and above-sensor T\textsubscript{air} and humidity conditions are defined by the mid-latitude summer standard atmosphere when daytime T\textsubscript{air, max} \textgreater 10 \si{\degreeCelsius} (the mid-latitude winter profile is substituted on days where T\textsubscript{air, max} \textless 10 \si{\degreeCelsius}) \citep{Kantor1962}.

In this method, a "typical" longwave bandpass, approximately 250 - 2300 \si{\centi\meter^{-1}} (4 - 42 \si{\micro\meter}), was extended to include much smaller wavenumber (longer wavelengths). This was done for two reasons: 1) To accurately represent broadband spectral longwave emission curves, which show significant emittance in wavenumber smaller than 250 \si{cm^{-1}} (wavelengths much longer than 42 \si{\micro\meter}). 2) To replicate the spectral signal "seen" by a silicone-domed pyrgeometer, which continues to transmit radiation at wavenumber \textless 250 \si{cm^{-1}} (wavelengths \textgreater 42 \si{\micro\meter}). A "typical" longwave bandpass underestimates a pyrgeometer signal by approximately 7 - 10 \si{\watt\per\square\meter}, depending on emitter temperature. A comparison of ‘typical’ and ‘extended’ longwave bandpasses is shown in Figure \ref{dometrans}.

\begin{figure}[H]
	\includegraphics[width=\textwidth]{dometrans}
	\caption{A comparison of dome transmittance for a Kipp \& Zonen silicone domed pyrgeometer (data supplied by Kipp \& Zonen \textit{pers. comm.}) and at-sensor radiance (T\textsubscript{surf} = 300 \si{K}, T\textsubscript{air} = 300 \si{K}, $z$ = 30 \si{m})  for "typical" and extended bandpasses.}
	\label{dometrans}
\end{figure}

@@

\noindent to yield a directional radiance $ L'_z $ for each $\theta$ over a waveband of $\nu_1 $= 0 \si{\per\centi\meter} to $\nu_2$ = 2300 \si{cm^{-1}}. $ \overline{r} $ is Planck weighted mean broadband sensor response computed as,

\noindent where $ R(\lambda) $ is spectral radiance computed from a Planck function at an approximated emitter temperature and $r (\theta)$ is spectral sensor response.

$ L'_z (\theta) $ are then multiplied by their associated angular view factor weighting ($\Phi$) and integrated over the hemisphere to yield an irradiance $ L_z $ for the target T\textsubscript{hem, r}

@@

$L_z (T\textsubscript{spec}) $ is representative of at-sensor irradiance upwelling from the urban surface described in SUM at the target specified temperature T\textsubscript{hem, r} for the measured T\textsubscript{air}, humidity, aerosol, and trace gas profile. The process is repeated to retrieve $L_z$ for the range of potential T\textsubscript{hem, r} at the given time-step. Irradiance - T\textsubscript{hem, r} pairings are then aggregated into a LUT. Finally, the measured irradiance is matched with its closest modeled irradiance to yield an atmospherically corrected, radiometric hemispherical surface temperature for the given time step. The workflow is repeated at 30 \si{\minute} intervals to yield a continuous time series of T\textsubscript{hem, r}. Atmospheric correction magnitudes can then be calculated as the difference between T\textsubscript{hem, r} and T\textsubscript{hem, b}, with T\textsubscript{hem, b} calculated via equation \ref{stefb1}.

\section{Evaluation of the method using profiles of upwelling longwave radiation over a homogeneous flat surface} \label{sensitivity}
